\chapter{Related Work and State of the Art}
\label{cap:estat}

Melanoma, a type of cancer that arises from melanin-producing cells, can be
found in various parts of the body such as the skin, eyes, nerve centers, and
meninges. Early diagnosis is crucial for improving the chances of curing
melanoma, even though it has the highest increasing incidence rate among all
skin cancer types. According to a study \cite{TimelyMelanomaDetection}, timely
identification of early-stage skin cancer resulted in a significant 90\%
reduction in mortality rates. For instance, patients diagnosed with stage I
melanoma have a 10-year overall survival probability ranging from 94\% to 98\%,
while those in stage IV have a much lower estimated 10-year overall survival
rate of just 10\% to 15\%. \\

Dermoscopy is a non-surgical method used to examine the underlying layers of
the skin. While it can yield good results, it requires extensive training and
experience in dermatology. However, it may not provide a definitive diagnosis
for melanoma, especially in its early stages. Consequently, there is a need for
an automated diagnostic tool. \\

In \cite{EpidemiologySkinCancer} study, the melanoma task classification was
compared between expert opinions and artificial neural networks. The computer
program demonstrated had an area under the receiver operating characteristic
curve of 0.87, which was higher than the dermatologists (0.74), the program
also had a higher sensitivity in classification of 85\% against the 76\% by the
dermatologists. These findings indicate the potential utilization of automated
systems in the field of skin cancer detection. \\

For cancer prediction, a supervised learning approach is employed. The most
common algorithms or methodologies include decision trees, convolutional neural
networks (CNN), support vector machines (SVM), k-nearest neighbors (KNN) and
Transformers. One of the most powerful systems are CNNs (Convolutional Neural
Networks), despite the fact that their use may involve a loss of
explainability, which is a major concern in healthcare systems. \\

Although this project goes beyond the mere creation of highly accurate models
for classifying melanoma, we have taken into consideration and reviewed related
works that have influenced and guided our own path.

\section{Identifying Melanoma Images Using EfficientNet Ensemble}

The winning approach to the 2020 SIIM-ISIC Melanoma Classification Challenge
\cite{ISICKaggle}. The team not only let the competition source code available
on GitHub \cite{WinningISICGithub} but they also wrote a paper explaining in
detail their investigation \cite{WinningISIC}. \\

The SIIM-ISIC Melanoma Classification Challenge was conquered by this ensemble of
convolutional neural networks (CNN). The winning solution involved training 16
EfficientNets, along with a ResNext101 and a ResNet101. To create this ensemble
of models, various strategies were employed, including utilizing patients'
metadata in addition to dermoscopy images, training models with different input
image sizes, and even training the models for varying numbers of epochs
\cite{WinningISIC}.

\begin{itemize}
  \item Implementation of a stable validation scheme.
  \item Effective selection of the model target.
  \item Thoughtful optimization of the pipeline.
  \item Utilization of ensemble learning with highly diverse models.
\end{itemize}

The submission that won achieved an AUC (Area Under the Curve)\footnote{AUC is
a metric that quantifies the overall quality of a binary classification model
by measuring the area under its ROC curve. It provides a single value that
summarizes the model's ability to discriminate between positive and negative
instances.} score of 0.9600 on cross-validation and 0.9490 on the private
leaderboard. \\

From their work, we adopted various deep learning techniques. For instance, we
applied the same way they evaluate models given an unbalanced multi-class
data-sets like as the ISIC dataset is. To properly assess the training process,
they utilized the AUC with one-vs-rest (OvR) metric. This project as well uses
this metric to evaluate the performance of the models. \\

Another aspect the current thesis borrowed from this work is the approach to
cleaning and mapping data-sets from different years. They trained their models
with different input image sizes, but the process of mapping and joining the
data-sets into a single data-set was similar to our approach, where we
consistently mapped the data into eight different classes. \\

The pipeline of data augmentation that is implemented in the work is also
reused. Equivalent to them, this thesis uses {\tt
albumentations}\cite{Albumentations} library instead of the native data
agumentation package provided from PyTorch. \\

These inspirations and adaptations from the related work has greatly influenced
the development and organization of this deep learning project.

\section{CNN Explainer}

CNN explainer is a web page created through a collaborative research effort
between Georgia Tech and Oregon State\cite{CNNExplainer}. It leverages
TensorFlow.js, a deep learning library that utilizes GPU acceleration within
the web browser, to load pretrained models for visualization. The entire
interactive system is implemented in JavaScript, utilizing Svelte as a
framework and D3.js for visualizations. With CNN Explainer, users can upload
images and obtain predictions for those images across ten different classes.
\\

While CNN Explainer primarily aims to serve educational purposes, the UI of the
current thesis, focuses on providing dermoscopy images predictions and
information about the models used and their outputs. The inspiration for
incorporating an interactive UI for end users stemmed from CNN Explainer.
Consequently, we utilized the same web framework to develop the UI.

\section{Dermatologist-level Classification of Skin Cancer with
Deep Neural Networks}

This study demonstrated the use of a deep learning algorithm to classify skin
lesions, including melanoma, with accuracy comparable to dermatologists. The
deep neural network was trained on a large dataset of images and achieved high
sensitivity and specificity \cite{SkinCancerDeepNN}.

\section{Computerized Analysis of Pigmented Skin Lesions: A
Review}

The goal of this paper is to review the papers on computerized analysis of
dermoscopy and clinical images of pigmented skin lesions. The paper also
clarifies terminology that is often misused in the literature, and it also
organizes and group together useful sources, making it easier to find
information on a particular sub-topic when searching through the existing
literature \cite{MelanomaTopicsReview}.
