\chapter{Results}
\label{cap:result}

In this chapter, we present the results of various machine learning
approaches used to train the models discussed in \textit{Chapter \ref{cap:contrib}}.
These results are presented using tables and visualizations to
facilitate understanding the benefits and limitations of each decision. The tables and visualizations,
provide a concise and comparative summary of the performance metrics, such as accuracy, AUC and recall. \\

Additionally, we showcase the outcomes of the CAD infrastructure constructed around this thesis.


\section{Metrics}

After training each model and inferring the predictions,
we saved the metrics of interest for each dataset (train, validate, test).
The training information of each training approach is given in \textit{Table \ref{table:trained-models-information}}.
On the other hand, \textit{Table \ref{table:resume-metrics}} provides a summary of the metrics acquired for each model in the different datasets. \\

The accuracy metric in \textit{Table \ref{table:resume-metrics}} represents how well
the model performs in an unbalanced multiclass classification problem with 8 different labels.
Meanwhile, AUC and recall specifically indicate how well the model is performing
in classifying melanoma from the other classes. \\


The metrics that have a gray background in \textit{Table \ref{table:resume-metrics}} are from models that had extra regularization techniques,
such as dropout or data augmentation. Additionally, it is important to
mention that validation and test metrics were obtained using the Test-Time Augmentation technique,
which, as explained in previous chapters, behaves as an ensemble.

\newpage

\begin{landscape}

\begin{table}
\centering
\begin{tabular}{lccccccccc}
    \toprule
 & Train Acc & Val Acc & Test Acc & Train AUC & Val AUC &  Test AUC & Train Recall & Val Recall &  Test Recall \\
 \midrule
M0 & 0.835 & 0.778 & 0.772 & 0.952 & 0.903 & 0.892 & 0.756 & 0.676 & 0.652 \\
M1 & 0.829 & 0.779 & 0.771 & 0.947 & 0.900 & 0.891 & 0.695 & 0.633 & 0.599 \\
M2 & 0.808 & 0.765 & 0.762 & 0.933 & 0.895 & 0.885 & 0.658 & 0.609 & 0.582 \\
M3 & 0.811 & 0.767 & 0.764 & 0.935 & 0.896 & 0.886 & 0.663 & 0.605 & 0.589 \\
\cellcolor{gray!50}M4 & \cellcolor{gray!50}0.757 & \cellcolor{gray!50}0.750 & \cellcolor{gray!50}0.741 &  \cellcolor{gray!50}0.886 & \cellcolor{gray!50}0.877 & \cellcolor{gray!50}0.858 & \cellcolor{gray!50}0.478 & \cellcolor{gray!50}0.475 & \cellcolor{gray!50}0.446  \\
\cellcolor{gray!50}M5 & \cellcolor{gray!50}0.728 & \cellcolor{gray!50}0.717 &  \cellcolor{gray!50}0.715 & \cellcolor{gray!50}0.867 & \cellcolor{gray!50}0.861 & \cellcolor{gray!50}0.842 & \cellcolor{gray!50}0.423 & \cellcolor{gray!50}0.403 & \cellcolor{gray!50}0.395  \\
\cellcolor{gray!50}M6 & \cellcolor{gray!50} & \cellcolor{gray!50}SLR &  \cellcolor{gray!50} & \cellcolor{gray!50}M0 & \cellcolor{gray!50}M1 & \cellcolor{gray!50}M2 & \cellcolor{gray!50}M0 & \cellcolor{gray!50}M1 & \cellcolor{gray!50}M2  \\
\cellcolor{gray!50}M7 & \cellcolor{gray!50} & \cellcolor{gray!50}SLR &  \cellcolor{gray!50} & \cellcolor{gray!50}M0 & \cellcolor{gray!50}M1 & \cellcolor{gray!50}M2 & \cellcolor{gray!50}M0 & \cellcolor{gray!50}M1 & \cellcolor{gray!50}M2  \\
\bottomrule
\end{tabular}
\caption[Training Information For Each Model.]
  {\textit{Training Information For Each Model. Empty spaces represent non-use of that feature.
  Table by Author}}
{\label{table:resume-metrics}}
\end{table}

\end{landscape}
