\section{Manual Installation}
\label{appendix:appendix_a}

We will provide you with the necessary tools to install the CAD infrastructure.
You won't have to worry about managing the installation of Python packages and NPM packages,
as we have created images that include all the required packages for seamless execution. \\

Although you need some tools for the installation process,
these tools are specifically for building the project and are independent of the services created. \\

This example employs Fedora Linux 38 as the operating system; however,
all the tools used for building the platform are cross-platform, ensuring smooth execution on other operating systems as well. \\

The tools you will need for the installation are these:

\begin{itemize}
  \item Git
  \item Docker or Podman
  \item docker-compose
  \item CURL
\end{itemize}

Make sure you have all the tools listed
in the requirements. Then, First thing you need to do be a super user.

\begin{Verbatim}[fontsize=\small]
$ sudo su
\end{Verbatim}

If you are using Docker.

\begin{Verbatim}[fontsize=\small]
$ curl https://gitlab.com/wilberquito/open.thesis/-/raw/main/MAKE.sh | bash
\end{Verbatim}

If you are using Podman, you need to install
the podman docker package to allow Podman work
natively with Docker commands.

\begin{Verbatim}[fontsize=\small]
$ sudo dnf install -y podman-docker
\end{Verbatim}

And then you can use the MAKE.sh script to build the architecture.

\begin{Verbatim}[fontsize=\small]
$ curl https://gitlab.com/wilberquito/open.thesis/-/raw/main/MAKE.sh | bash
\end{Verbatim}
